### 2018-07-27 chapters/01-introduction/intro.tex
Implement howard suggestions for the first 2 pages

A typical workflow of a scientist who writes a scientific publication is to use a \gls*{wp} to write the paper and one or more \gls*{cas} for verification, analysis and visualization. Especially in \gls*{stem} literature, \LaTeX\footnote{Note that technically \LaTeX{} is not a \gls*{wp} (\url{https://www.latex-project.org/about/}, seen 07/2017) like \textit{Microsoft Word}. However, since \LaTeX{} (an extension of \TeX) is the standard to write articles in \gls*{stem} and we only focus on mathematical writings in this paper, we categorize \LaTeX{} as a \gls*{wp} as well.} has become the de facto standard for writing scientific publications over the past 30 years~\parencites{LATEX:Standard}[559]{DigitalTypo}{Knuth}. \LaTeX{} enables printing of mathematical formulae in a structure similar to handwritten style. For example, consider the Jacobi polynomial~\parencite[18.3 in table 1]{NIST:DLMF}
\begin{equation}\label{eq:P}
P_n^{(\alpha , \beta)}(\cos(a\Theta)),
\end{equation}
where $\alpha, \beta > -1$, and $n$ a nonnegative integer. 
This formula is written in \LaTeX{} as
\begin{equation*}
\verb|P_n^{(\alpha,\beta)}(\cos(a\Theta))|.
\end{equation*}

While \LaTeX{} focuses on displaying mathematics, a \gls*{cas} concentrates on computations and user friendly syntax. Especially important for a CAS is to embed unambiguous semantic information within the input. Each system uses different representations and syntax in consequence. Hence, a writer needs to constantly translate mathematical expressions from one representation to another and back again. Table~\ref{tab:JacobiP-usecase} shows four different representations for the same formula~(\ref{eq:P}).

\begin{table}[ht]
	\centering
	\begin{tabular}{ll}
		\hline
		Systems & Representations \\
		\hline
		\hline
		Generic \LaTeX\ & \verb|P_n^{(\alpha,\beta)}(\cos(a\Theta))| \\ 
		Semantic \LaTeX\ & \verb|\JacobiP{\alpha}{\beta}{n}@{\cos@{a\Theta}}| \\
		\Maple & \verb|JacobiP(n,alpha,beta,cos(a*Theta))| \\ 
		\Mathematica & \verb|JacobiP[n,\[Alpha],\[Beta],Cos[a \[CapitalTheta]]]|\\
		\hline
	\end{tabular}
	\caption{Different representations for the same mathematical formula~(\ref{eq:P}). Generic \LaTeX{} is the default \LaTeX{} expression. Semantic \LaTeX{} uses special semantic macros to embed semantic information.}
	\label{tab:JacobiP-usecase}
\end{table}

Translations from generic \LaTeX{} to \gls*{cas} are difficult to realize since the semantic information is not explicitly given in the input. The \gls*{nist} has created a set of semantic \LaTeX{} macros~\cite{DLMF:Macros}. Each macro ties specific character sequences to a well-defined mathematical object and is linked with the corresponding definition in the \gls*{dlmf} or \gls*{drmf}. These macros embed necessary semantic information into \LaTeX{} expressions. One example of such a macro is given table~\ref{tab:JacobiP-usecase} for the semantic \LaTeX{} representation for the Jacobi polynomial. The macros provide isolated access to important parts of the mathematical function, such as the arguments.

>>>>

A typical workflow of a scientist who writes a scientific publication is to use a \gls*{wp} to write the paper and one or more \gls*{cas} for verification, analysis and visualization. Especially in the \gls*{stem} literature, \LaTeX\footnote{Note that technically \LaTeX{} is not a \gls*{wp} (\url{https://www.latex-project.org/about/}, seen 07/2017) like \textit{Microsoft Word}. However, since \LaTeX{} (an extension of \TeX) is the de facto standard for writing articles in \gls*{stem}, and we only focus on mathematical writing in this paper, we have categorize \LaTeX{} as a \gls*{wp} as well.} has become the de facto standard for writing scientific publications over the past 30 years~\parencites{Knuth}[559]{DigitalTypo}{LATEX:Standard}. \LaTeX{} enables printing of mathematical formulae in a structure similar to handwritten style. For example, consider the specific Jacobi polynomial~\parencite[18.3 in table 1]{NIST:DLMF}
\begin{equation}\label{eq:P}
P_n^{(\alpha , \beta)}(\cos(a\Theta)),
\end{equation}
where $\alpha, \beta > -1$, and $n$ is a nonnegative integer. 
This mathematical expression is written in \LaTeX{} as
\begin{equation*}
\verb|P_n^{(\alpha,\beta)}(\cos(a\Theta))|.
\end{equation*}

While \LaTeX{} focuses on displaying mathematics, a \gls*{cas} concentrates on computations and user friendly syntax. Especially important for a CAS is to embed unambiguous semantic information within the input. Each system uses different representations and syntax in consequence. Hence, a writer needs to constantly translate mathematical expressions from one representation to another and back again. Table~\ref{tab:JacobiP-usecase} shows four different representations for~(\ref{eq:P}).

\begin{table}[ht]
	\centering
	\begin{tabular}{ll}
		\hline
		Systems & Representations \\
		\hline
		\hline
		Generic \LaTeX\ & \verb|P_n^{(\alpha,\beta)}(\cos(a\Theta))| \\ 
		Semantic \LaTeX\ & \verb|\JacobiP{\alpha}{\beta}{n}@{\cos@{a\Theta}}| \\
		\Maple & \verb|JacobiP(n,alpha,beta,cos(a*Theta))| \\ 
		\Mathematica & \verb|JacobiP[n,\[Alpha],\[Beta],Cos[a \[CapitalTheta]]]|\\
		\hline
	\end{tabular}
	\caption{Different representations for~\eqref{eq:P}. Generic \LaTeX{} is the default \LaTeX{} expression; semantic \LaTeX{} uses special semantic macros to embed semantic information; and \gls*{cas} representations are unique to themselves.}
	\label{tab:JacobiP-usecase}
\end{table}

Translations from generic \LaTeX{} to \gls*{cas} are difficult to realize since the full semantic information is not easily constructed from the input. Bruce Miller at the \gls*{nist} has created a set of semantic \LaTeX{} macros~\parencite{DLMF:Macros}. Each macro ties specific character sequences to a well-defined mathematical object and is linked with the corresponding definition in the \gls*{dlmf}. The \gls*{drmf} is an outgrowth of the \gls*{dlmf} with the goal to facilitate interaction among a community of mathematicians and scientists~\parencites{DRMF:14}{DRMF:15}. The \gls*{drmf} extends the set of semantic macros. These macros embed necessary semantic information into \LaTeX{} expressions. One example of such a macro is given Table~\ref{tab:JacobiP-usecase} for the semantic \LaTeX{} representation for the Jacobi polynomial. The macros provide isolated access to important parts of the mathematical function, such as the arguments.
